%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Edwin Mei's CV
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{MEI, Yue} % Name
\address{HomePage: https://tuoye25.github.io/} % Home
\address{BusinessCard: https://bonjour.bio/edwinm/} % Busines Card
\address{Phone\#: (+86)~$\cdot$~18964070908} % Phone number
\address{Email: edwin\_mei-yue@foxmail.com} % Email

\begin{document}

%----------------------------------------------------------------------------------------
%	SELF-INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Self-Introduction}
    This is Edwin, currently working as a Senior AI Development Engineer while serving as CTO for a side venture where I lead technical decision-making and architecture design. My research focused on computer vision and model optimization, with a first-author paper published at ICICML 2023 on knowledge distillation in deep reinforcement learning. Previously, I worked on the Azure Cloud Architecture team at Microsoft and led data analytics and full-stack development at FNZ. I am proficient with PyTorch, TensorFlow, LangGraph, and various AI Agent frameworks including Claude, DeepSeek, and Multica. I look forward to combining my research background and engineering experience to deliver impactful AI solutions.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

    {\bf The Northeastern University, ME, USA} \hfill {\em June 2025} \\
    M.S. in Computer Science \hfill Overall GPA: \textbf {4.0}

    {\bf The Ohio State University, OH, USA} \hfill {\em June 2019} \\
    B.S. in Electrical \& Computer Engineering \hfill Minor in Mathematics

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

    \begin{rSubsection}{Qunxian Group}{Jun 2026 - Present}{Senior AI Development Engineer}{Shanghai, China}
        \item Lead the company's digital transformation strategy, responsible for AI technical architecture design and implementation.
        \item Guilin Factory AI Data Foundation: Design and build an industrial-grade AI data foundation, integrating multi-source heterogeneous production data, responsible for model training and performance optimization, achieving intelligent upgrading of production processes.
        \item ERP System Design and Optimization: Lead the intelligent transformation of the ERP system, embedding AI capabilities into core business processes, improving supply chain management and resource allocation efficiency.
        \item OA Platform AI Transformation: Drive the intelligent upgrading of the company's OA system, integrating AI functions such as intelligent approval, knowledge Q\&A, and process automation, significantly improving office efficiency.
    \end{rSubsection}

    \begin{rSubsection}{Digital Factory (Side Business)}{Jan 2026 - Present}{Co-founder \& CTO}{Shanghai, China}
        \item Lead the construction of a distributed AI factory system based on multi-agent collaboration, responsible for overall technical architecture design and AI model orchestration.
        \item Design and implement hybrid cloud-on-premises inference architecture, integrating multiple large models including Claude Code, DeepSeek V4 Pro, and Qwen (distilled from Opus 4.7). Achieve local low-cost inference through Ollama, optimizing response speed and computing costs.
        \item Build a multi-Agent collaboration framework using Multica + OpenClaw, scheduling digital employees like Hermes and QoderWake to process complex tasks in parallel, enabling an automated pipeline for game design operations.
        \item Establish the technical infrastructure from scratch, covering core modules including AI inference, task orchestration, and multi-model routing.
        \item Expand the business from game design to multiple verticals including group buying, demonstrating strong system portability and horizontal scalability.
    \end{rSubsection}

    \begin{rSubsection}{FNZ Information Technology}{Dec 2021 - July 2022}{Analyst Developer}{Shanghai, China}
        \item Worked as a full-stack engineer in agile software development with a focus on the Core Repository - FNZOneX.
        \item Added a new Adviser group to previous Administrator and Guest groups \& modified Declaration scripts from Alchemist based on user permission matrix.
        \item Embedded Address Lookup API from 3rd party Addressy into all address fields on the website.
        \item Produced runtime SQL script sets for multiple development/test environments.
        \item Debugged JavaScript errors from Elements, Console, Sources and Network through browser inspections; utilized Visual Studio debug mode to track aspx/aspx.vb errors.
        \item Set up, modified and shared IIS server configuration for development and demonstration.
        \item Collaborated with global IT department and cross-team peers to solve jurisdictional issues.
        \item Resolved showstoppers \& release issues from testers and formulated testing procedure before functional review
    \end{rSubsection}

    \begin{rSubsection}{Wicresoft Co. Ltd.(Microsoft GCR)}{Oct 2019 - Dec 2021}{Technical Cloud Engineer \& Technical Advisor}{Shanghai, China}
        \item Specialized in Azure Monitor, Log Analytics, Automation \& App Insights.
        \item Customized alert configuration, query search, data sampling \& performance counter collection.
        \item Captured \& analyzed NetMon, ProcMon \& Fiddler traces to troubleshoot issues on agents, hybrid workers and portals; visualized data through Azure dashboard, Metric Explorer \& workbook.
        \item Debugged Application Insights SDK configuration scripts in .Net/.Net Core/Java/Python/JavaScript with Visual Studio/VS Code.
        \item Helped design, modify and debug PowerShell/Python/PS workflow/graphical Runbooks \& DSC configuration; advised on partner integration and workspace solutions, e.g. Update Management, Auto Start/Stop VMs, Change Tracking and Inventory
        \item Served key clients such as Adobe, Intel, and Amazon and dealt with risky or long-term case escalations.
        \item Monitored technical work of 12 team members in Shanghai, Wuxi and Beijing; resolved scoping confliction between our team and other teams.
        \item Cooperated with Team leader and Partner TA on case analysis, employee recruitment \& team planning.
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Project}

    \begin{rSubsection}{Dataset Distillation of Galaxy CNN}{Sep 2024 - Dec 2025}{Inst. Tala Talaei Khoei}{NEU}
        \item Demonstrated superior performance in tasks like galaxy morphology classification by using a distilled and curated version of the newest Galaxy Zoo dataset.
        \item Careful tuning of statistical significance thresholds for validation loss trends to optimize performance.
        \item Used STM to prevent overfitting and accelerate the learning process.
        \item Offered higher classification accuracy and more efficient training, while mitigated class imbalance and improved overall data quality.
    \end{rSubsection}

    \begin{rSubsection}{Knowledge Distillation of Deep Reinforcement Learning}{Jul 2023 - Sep 2023}{Inst. Mark Vogelsberger}{MIT}
        \item Built teacher and student DQN models for deep reinforcement learning using PyTorch.
        \item Carried out comparative experiments in CartPole, MountainCar, Acrobot, LunarLander and Pendulum environments from Gymnasium.
        \item Systematically tuned hyperparameters (temperature, regression rounds) to evaluate knowledge distillation efficiency across different MDPs.
        \item Extended knowledge distillation to Deep Recurrent Q-Networks (DRQN) for more complex sequential decision-making tasks.
        \item The core findings of this project were published as a full paper at ICICML 2023: \\https://doi.org/10.1109/ICICML60161.2023.10424889
    \end{rSubsection}

    \begin{rSubsection}{Capstone : Solar Panel Validation Device}{Jan 2019 - Apr 2019}{Inst. Haskell Jac Fought}{OSU}
        \item Developed a Bluetooth serial communication module on Android Studio.
        \item Designed software requirements, features and behavior charts.
        \item Converted Arduino coding to Android.
    \end{rSubsection}

    \begin{rSubsection}{Advanced Energy Vehicle Design-and-Build Project}{Jan 2016 - May 2016}{Inst. Lauren Corrigan}{OSU}
        \item Coded Arduino through Arduino Integrated Development Editor.
        \item Used Solid Works to design components of Arduino with its size and shape controlled precisely.
        \item Recorded Arduino performance and helped improve its air dynamic efficiency.
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	CO-OP & PART-TIME SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Co-op \& Part-time}

    \begin{rSubsection}{NEU Machine Learning Course}{Jan 2025 - May 2025}{Teaching Assistant}{Maine, USA}
        \item Guided students to familiarize themself with various types of machine learning models \& correpsonding technics.
        \item Discussed with professor about the allocation of courses; answered questions and graded assignments in office hours.
    \end{rSubsection}

    \begin{rSubsection}{OSU ECE Department Laboratory}{Sep 2018 - Dec 2018}{Monitor \& Grader}{Ohio, USA}
        \item Guided students to practise coding with TI MPS430 series micro-controller.
        \item Reviewed their weekly test papers and experiment reports.
    \end{rSubsection}

    \begin{rSubsection}{Huahong Jitong Smart System}{May 2018 - Jul 2018}{Software Development Engineer}{Shanghai, China}
        \item Mastered the structure, data flow, operation \& coding of Automatic-Fare-Collection(AFC) system.
        \item Improved the UI design and updated the traffic data for transit system of Xi'an Metro Line 1-Line 4.
        \item Contributed to the database transfer from Oracle SQL to DB2.
    \end{rSubsection}

    \begin{rSubsection}{CEFC China Energy}{May 2017 - Jul 2017}{Information System Engineer}{Shanghai, China}
        \item Developed an intelligent OA schedule to interact with CEFC APP(Android / IOS).
        \item Designed an Access VBA instruction set to calculate bills with filtering \& tabulation functions.
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILL
%----------------------------------------------------------------------------------------

\begin{rSection}{Skill}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{14cm} }
        Languages           & Python, C\#, Java, C++, Golang, Shell, JavaScript, M, VBA, VHDL       \\
        ML Frameworks       & PyTorch, TensorFlow, Keras, Scikit-learn, LangGraph                   \\
        Models \& AI Tools  & Claude, Codex, DeepSeek, Pi, Wan, Flux, Kling, Seedance               \\
        AI Agent Frameworks & Multica, HiClaw, PaperClips, Hermes                                   \\
        Model Optimization  & Knowledge Distillation, Quantization, Pruning, Inference Acceleration \\
        Databases           & Microsoft SQL, KQL, MySQL, MongoDB, SQLite                            \\
        Cloud               & Azure, AWS, Distributed Systems, Microservices                        \\
        Dev Tools           & VS, VS Code, Git, Docker, SQL Server, Kusto, TailScale                \\
        Hardware            & Arduino, Multiplexers, PLDs, Clocked Sequential Circuits, VLSI        \\
    \end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	COURSEWORK
%----------------------------------------------------------------------------------------

\begin{rSection}{Coursework}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{12cm} }
        Computer   & Machine Learning, Database Management Sys, Algorithms, Cloud Computing, Software Development \& Design, Operating Systems, Computer Architecture \& Design, Computer Organization \& Embedded Systems                            \\
        Electrical & Analog Systems \& Circuits, Signal \& Systems, Digital Logic, Microcontrollers, Semiconductor Electronic Devices, Optical engineering, Feedback Control Systems, Advanced Digital Design, VLSI Digital Signal Processing Systems \\
        Math       & Calculus for Scientists \& Engineers, Linear Algebra, Higher Mathematics, Numerical Analysis, Partial Differential Equations                                                                                                     \\
        Others     & Engineering Economic Decisions, Engineering Ethics, Probability and Statistics                                                                                                                                                   \\
    \end{tabular}

\end{rSection}

% %----------------------------------------------------------------------------------------
% %	HOBBIES & INTERESTS
% %----------------------------------------------------------------------------------------

% \begin{rSection}{Hobbies \& Interests}
%   Outside of work, I enjoy a balanced mix of activities. On the active side, I'm passionate about pickleball and badminton, where I love the fast rallies and team dynamics. On the intellectual side, I'm an avid fan of escape rooms, murder mystery games, and board games—immersing myself in rich narratives and strategic thinking. These hobbies have taught me that great AI products, much like great game design, require deep empathy for users and meticulous attention to detail. Looking forward to connecting with colleagues over a match or a game session outside of work.
% \end{rSection}

\end{document}